--- 
title: "A Taxonomy of Data Synthesis: A Tutorial"
author: 
    
  - name        : Emorie D. Beck
    affiliation : Feinberg School of Medicine
  - name        : Emily C. Willroth
    affiliation : Feinberg School of Medicine
  - name        : Daniel K. Mroczek
    affiliation : Feinberg School of Medicine, Northwestern University
  - name        : Eileen K. Graham
    affiliation : Feinberg School of Medicine
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\ %B %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
editor_options: 
  chunk_output_type: console
---

# Workspace  

Placeholder


## Packages  
## Directory Path  
## Codebook  
## Navigating This Tutorial  

<!--chapter:end:index.Rmd-->


# Data Cleaning {#cleaning}

Placeholder


## Berlin Aging Study (BASE-I)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## Einstein Aging Study (EAS)  
### Load Data  
### Covariates  
## German Socioeconomic Panel (GSOEP)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## Household, Income, and Labour Dynamics in Australia (HILDA)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## Health and Retirement Study (HRS)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## Longitudinal Aging Study Amsterdam (LASA)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## RUSH Memory and and Aging Project (MAP)  
## RUSH Minority Aging Reseach Study (MARS)  
## RUSH Religious Orders Study (ROS)  
## Origins of the Variances of the Oldest-Old: Octogenarian Twins (OCTO-TWIN)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## Swedish Adoption Twin Study of Aging (SATSA)  
### Load Data  
### Recoding & Reverse Scoring  
### Covariates  
### Personality Variables  
### Outcome Variables  
### Combine Data  
## Seattle Longitudinal Study (SLS)  

<!--chapter:end:01-data-cleaning.Rmd-->


# Method 1: Pooled One Stage Models without Study-Specific Effects {#runmodels}

Placeholder


## Step 1: Combine Data  
### Study-Level Moderators  
### Harmonize Data  
### Save Data Files  
## Step 2: Run Models and Extract Results  
### Method 1A: Linear Regression  
#### Model Function   
#### Simple Effects Function  
#### Run Models and Summaries  
#### Compile Results  
##### Tables  
###### Fixed Effects  
###### Study-Specific Effects  
###### Heterogeneity Estimates  
##### Figures  
###### Overall Forest  
###### Study-Specific Forest Plots  
###### Overall Simple Effects Plots  
###### Study-Specific Simple Effects Plots  
### Part 1B: Pooled Linear Regression with Cluster Robust Standard Errors  
#### Model Function  
#### Run Models and Summaries  
#### Compile Results  
##### Tables  
###### Fixed Effects  
###### Study-Specific Effects  
###### Heterogeneity Estimates  
##### Figures  
###### Overall Forest  
###### Study-Specific Forest Plots  
###### Overall Simple Effects Plots  
###### Study-Specific Simple Effects Plots  

<!--chapter:end:02-IPD_reg.Rmd-->


# Method 2: Pooled One Stage Models with Study-Specific Effects  

Placeholder


## Step 1: Combine Data  
### Study-Level Moderators  
### Harmonize Data  
### Save Data Files  
## Step 2: Run Models and Extract Results  
### Method 2A: Pooled One Stage Models with Dummy Codes  
#### Model Function   
#### Contrasts Function   
#### Study-Specific Effects Function  
#### Run Models and Summaries  
#### Compile Results  
##### Tables  
###### Fixed Effects  
###### Study-Specific Effects  
##### Figures  
###### Fixed Effects  
###### Study-Specific Effects  
### Method 2B: Pooled One Stage Models with Random Effects  
#### Model Function  
#### Study-Specific Effects Function  
#### Heterogeneity Estimates Function   
#### Run Models and Summaries  
#### Compile Results  
##### Tables  
###### Fixed Effects  
###### Study-Specific Effects  
###### Heterogeneity Estimates  
##### Figures  
###### Fixed Effects  
###### Study-Specific Effects  

<!--chapter:end:03-IPD_mega.Rmd-->

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Method 3: Two-Stage Individual Participant Meta-Analysis  

## Step 1: Combine Data  
We again need to combine data. However, rather than combining data across studies, for the two-stage approach, we'll be combining data within studies in order to run separate analyses for each before combining via meta-analytic tools.  
```{r 2 stage ipd meta load combined data}
loadRData <- function(fileName, type){
#loads an RData file, and returns it
    path <- sprintf("%s/data/clean/%s_cleaned.RData", res_path, fileName)
    load(path)
    get(ls()[grepl(type, ls())])
}

ipd_meta_data <- tibble(
  study = studies[studies %in% c("HRS", "GSOEP", "SATSA", "HILDA", "LASA", "BASE-I", "OCTO-TWIN")]
  , data = map(str_to_lower(study), ~loadRData(., "combined"))
  ) %>% mutate(
    data = map(data, ~(.) %>% 
                 ungroup() %>% 
                 mutate(SID = as.character(SID)))
    , study = mapvalues(study, studies, studies_long)
  ) %>%
  unnest(data) %>%
  mutate(age = ifelse(is.na(age), p_year - yearBrth, age))

ipd_meta_data
```

### Study-Level Moderators  
```{r ipd reg moder harmonization}
save_fun <- function(d, trait, outcome){
  save(d, file = sprintf("%s/data/two_stage/meta_data/%s_%s.RData", wd, trait, outcome))
}

ipd_metaMod_data <- sprintf("%s/codebooks/crystallized_tables.xlsx", res_path) %>% 
  read_xlsx(., sheet = "Table 4") %>%
  select(-Category, -Construct, -category) %>%
  pivot_longer(cols = c("BASE-I":"SATSA")
               , names_to = "study"
               , values_to = "value") %>%
  pivot_wider(names_from = "name"
              , values_from = "value") %>%
  right_join(
    ipd_meta_data %>% 
      select(-p_value, -o_value, -(education:yearBrth))
    ) %>%
  group_by(study, Trait, Outcome) %>%
  mutate(baseAge = mean(age, na.rm = T) - 60, # center at age 60
         predInt = mean(o_year - p_year) - 5, # center at 5 years
         baseYear = mean(p_year) - 2000) %>% # center at 2000
  ungroup() %>%
  select(Trait, Outcome, study, continent, country, scale, baseAge, baseYear, predInt) %>%
  distinct() %>%
  group_by(Trait, Outcome) %>%
  nest() %>%
  ungroup()
ipd_metaMod_data

ipd_metaMod_data %>% mutate(pmap(list(data, Trait, Outcome), save_fun))
```

### Harmonize Data  
```{r 2 stage ipd meta harmonization}
ipd_meta_data <- ipd_meta_data %>%
  group_by(study, Trait, Outcome) %>%
  mutate_at(vars(p_value, o_value, SRhealth), 
            ~((. - min(., na.rm = T))/(max(., na.rm = T) - min(., na.rm = T))*10)) %>%
  mutate(gender = factor(gender, levels = c(0,1), labels = c("Male", "Female")),
         education = education - 12,
         age = age - mean(age, na.rm = T)) %>% 
  ungroup()
ipd_meta_data
```

### Save Data Files  
```{r 2 stage ipd meta save data}
save_fun <- function(d, trait, outcome, study){
  save(d, file = sprintf("%s/data/two_stage/%s_%s_%s.RData", wd, trait, outcome, study))
}

ipd_meta_data %>%
  group_by(study, Trait, Outcome) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, Trait, Outcome, study), save_fun))
```

## Step 2: Run Models for Each Study  

### Model Function  
```{r 2 stage ipd meta study model function}
ipd3_study_mod_fun <- function(trait, outcome, type, mod, study, cov){
  ## load the data
  load(sprintf("%s/data/two_stage/%s_%s_%s.RData", wd, trait, outcome, study))
  
  ## compiled Bayesian model to speed up processing and avoid crashing
  if(type == "Bayesian") load(sprintf("%s/results/3_ipd_meta/bayes_sample_mod.RData", wd))
  
  ## model formula 
  if (cov == "all") cv <- c("age", "gender", "SRhealth")
  if (!cov %in% c("all", "none")) cv <- cov
  rhs <- "p_value"
  rhs <- if(cov != "none") c(rhs, cv) else rhs
  if(mod != "none"){rhs <- c(rhs, paste("p_value", mod, sep = "*"))}
  rhs <- paste(rhs, collapse = " + ")
  f <- paste("o_value ~ ", rhs, collapse = "")
  
  ## run the models & save
  m <- if(type == "Frequentist"){do.call("lm", list(formula = f, data = quote(d)))} else {update(m, formula = f, newdata = d)}
  save(m, file = sprintf("%s/results/3_ipd_meta/%s/studyModels/%s_%s_%s_%s_%s.RData"
                         , wd, type, outcome, trait, mod, cov, study))
  
  ## extract model terms and confidence intervals & save
  fx <- tidy(m, conf.int = T) %>%
    select(term, estimate, conf.low, conf.high)
  save(fx, file = sprintf("%s/results/3_ipd_meta/%s/studySummary/%s_%s_%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod, cov, study))
    
  ## calculate effect sizes for random effects meta analysis
  es <- ipd3_es_fun(m, type, mod)
  save(es, file = sprintf("%s/results/3_ipd_meta/%s/studyEffects/%s_%s_%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod, cov, study))
  
  ## clean up the local function environment
  rm(list = c("d", "f", "m", "fx", "es", "rhs"))
  gc()
}
```

### Effect Size Function  
```{r}
ipd3_es_fun <- function(m, type, mod){
  ## extract model features needed for meta-analysis
  ts <- insight::clean_parameters(m)$Cleaned_Parameter
  ts <- if(mod == "none") "p_value" else ts[grepl("p_value.", ts)]
  ts <- str_replace(ts, "[.]", ":")
  ## standardize the model 
  ms <- standardize(m)
  ## get standardized model coefficients and standard errors
  ## for bayesian models this is the sd of the posterior estimates
  es <- if(type == "Frequentist"){ 
    summary(ms)$coef[ts, c("Estimate", "Std. Error")] %>% setNames(c("Estimate", "SEI"))
    } else {
      fixef(ms)[ts, c("Estimate", "Est.Error")] %>% setNames(c("Estimate", "SEI"))
    }
  ## format to standardized format
  es <- es %>%
    t() %>% 
    as.data.frame() %>% 
    mutate(ni = if(type == "Frequentist") {nrow(m$model)} else {nrow(m$data)})
  return(es)
}
```


### Run Models  
```{r 2 stage ipd meta run model function}
done <- tibble(file = list.files(sprintf("%s/results/3_ipd_meta/Bayesian/studyModels", wd))) %>%
  separate(file, c("Outcome", "Trait", "Moderator", "Covariate", "study"), sep = "_") %>%
  mutate(study = str_remove_all(study, ".RData"),
         done = "done")
nested_ipd_reg <- tibble(files = list.files(sprintf("%s/data/two_stage", wd))) %>%
  separate(files, c("Trait", "Outcome", "study"), sep = "_") %>%
  mutate(study = str_remove(study, ".RData")) %>%
  left_join(
    crossing(
      study = studies[studies %in% c("HRS", "GSOEP", "SATSA", "HILDA", "LASA", "BASE-I", "OCTO-TWIN")]
      , Trait = traits$short_name
      , Outcome = outcomes$short_name
      , type = c("Frequentist", "Bayesian")
      , Moderator = c("age", "gender", "education", "SRhealth")
      , Covariate = c("none", "all")
    ) %>% 
      full_join(
        crossing(
          study = studies[studies %in% c("HRS", "GSOEP", "SATSA", "HILDA", "LASA", "BASE-I", "OCTO-TWIN")]
          , Trait = traits$short_name
          , Outcome = outcomes$short_name
          , type = c("Frequentist", "Bayesian")
          , Moderator = "none"
          , Covariate = c("none", "age", "gender", "education", "SRhealth", "all")
          )
        )
    ) %>%
  full_join(done) %>% filter(is.na(done)) %>%
  mutate(run = pmap(list(Trait, Outcome, type, Moderator, study, Covariate), ipd3_study_mod_fun))

```

## Step 3: Meta-Analyze Results  

### Functions  
#### Meta-Analysis Function  
```{r 2 stage ipd meta function}
ipd3_meta_fun <- function(es, type, trait, outcome, mod, cov){
  print(paste(type, trait, outcome, mod, cov))
  ## bayesian sample models for stability and speed
  if(type == "Bayesian") {
    mr <- if(mod %in% stdyModers$short_name) "metareg" else "meta"
    load(sprintf("%s/results/3_ipd_meta/bayes_sample_%s.RData", wd, mr))
  }
  
  ## adding meta-regression values to effect sizes
  if(mod %in% stdyModers$short_name) {
    load(sprintf("%s/data/two_stage/meta_data/%s_%s.RData",  wd, trait, outcome))
    es <- d %>% select(study, one_of(mod)) %>% 
      setNames(c("study", "metamod")) %>% 
      full_join(es) %>%
      mutate_if(is.character, factor)
  }
  
  ## base bayesian model
    # brm(formula = bf(Estimate | se(SEI) ~ 1 + (1 | study))
  #     , save_pars = "all"
  #     , sample_prior = T
  #     , prior = prior(cauchy(0,1), class = sd)
  #     , iter = 4000)
  
  ## base bayesian meta-regression model
  # update(mt
  #     , formula. = bf(~ . + metamod)
  #     , newdata = es
  #     , sample_prior = T)
  # run the meta-analytic model
  f <- if (mod %in% c("none", moders$short_name)) "Estimate ~ 1" else "Estimate ~ 1 + metamod"
  mt <- if(type == "Frequentist"){
    rma(formula(f)
        , sei = SEI
        , ni = ni
        , data = es)
  } else {
    if(!mod %in% stdyModers$short_name) {
      update(mt
             , newdata = es
             , sample_prior = T
             , cores = 4)
    } else {
      update(mt
             , formula. = bf(~ . + metamod)
             , newdata = es
             , sample_prior = T
             , cores = 4)
    }
  }
  save(mt, file = sprintf("%s/results/3_ipd_meta/%s/metaModels/%s_%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod, cov))
  
  # pull out and format the fixed effects (i.e. overall effects)
  fx <- ipd3_meta_fx_fun(mt, type, mod)
  save(fx, file = sprintf("%s/results/3_ipd_meta/%s/metaSummary/%s_%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod, cov))
  
  # pull out and format the cross-study heterogeneity estimates
  het <- ipd3_meta_rx_fun(mt, type)
  save(het, file = sprintf("%s/results/3_ipd_meta/%s/metaHetero/%s_%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod, cov))
  rm(list = c("mt", "es", "type", "trait", "outcome", "mod", "fx", "rx"))
  return(NULL)
}
```

#### Meta-Analysis Fixed Effect Function  
```{r 2 stage ipd meta table function}
ipd3_meta_fx_fun <- function(mt, type, mod){
  trgt <- if(mod %in% c("none", stdyModers$short_name)) "p_value" else paste0("p_value:", mod)
  if (type == "Frequentist"){
    coef(summary(mt)) %>%
      rownames_to_column("term") %>%
      select(term, estimate, SE = se, conf.low = ci.lb, conf.high = ci.ub) %>%
      mutate(study = "Meta-Analytic",
             term = mapvalues(term, "intrcpt", trgt))
  } else {
    fixef(mt) %>% data.frame() %>%
      rownames_to_column("term") %>%
      select(term, estimate = Estimate, SE = Est.Error, conf.low = Q2.5, conf.high = Q97.5) %>%
      mutate(study = "Meta-Analytic",
             term = mapvalues(term, "Intercept", trgt))
  }
}
```

#### Meta-Analysis Heterogeneity Function  
```{r 2 stage ipd meta table function}
ipd3_meta_rx_fun <- function(mt, type){
  if (type == "Frequentist"){
    ## for frequentist, we'll grab estimates of:
    ## - tau^2: estimated between-study heterogeneity
    ## - I^2: total hetero (tau^2) / total hetero + total var (tau^2 + sigma^2)
    ## - H^2: total var (tau^2 + sigma^2) / total sampling var (sigma^2)
    ## - QE: Chi^2 dist Cochran's Q statistic (hetero > 0)
    ## - QEp: associated p-value for QE for k df
    mt[c("tau2", "se.tau2", "I2", "H2", "QE", "QEp")] %>%
      ldply() %>%
      pivot_wider(names_from = ".id", values_from = "V1")
  } else {
    ## for Bayesian, we'll grab estimates of: 
    ## note, for these, we must estimate some directly
    ## but will use Bayes Factor to estimate probability of tau^2 > 0
    ## this should converge with other estimates but is more appropriate for Bayes
    ## - tau^2: average estimated between-study hetero across Bayes samples
    ## - I^2: total hetero (tau^2) / total hetero + total var (tau^2 + sigma^2)
    ## - H^2: total var (tau^2 + sigma^2) / total sampling var (sigma^2)
    ## - BF: posterior prob / prior prob
    tibble(tau2 = summary(mt)$random$study[,"Estimate"]^2
           , se.tau2 = summary(mt)$random$study[,"Est.Error"]^2
           , I2 = tau2 / (tau2 + var(resid(mt)[,"Estimate"]))
           , H2 = (tau2 + var(resid(mt)[,"Estimate"])) / var(resid(mt)[,"Estimate"])
           , BF = 1/hypothesis(mt, "study__Intercept^2 = 0", class = "sd")$hypothesis$Evid.Ratio
    )
  }
}
```

### Run Meta-Analysis and Meta-Regression Models  
```{r 2 stage ipd meta run}
loadRData <- function(fileName, type, obj, folder){
#loads an RData file, and returns it
    path <- sprintf("%s/results/3_ipd_meta/%s/%s/%s", wd, type, folder, fileName)
    load(path)
    get(ls()[grepl(obj, ls())])
}

## load in effect size data 
## first get file names
nested_ipd3_meta <- tibble(type = c("Frequentist", "Bayesian")) %>%
  mutate(file = map(type, ~list.files(sprintf("%s/results/3_ipd_meta/%s/studyEffects", wd, .)))) %>%
  unnest(file) %>%
  separate(file, c("Outcome", "Trait", "Moderator", "Covariate", "study"), sep = "_", remove = F) %>% 
  filter(!is.na(study)) %>%
  ## read in the files
  mutate(study = str_remove(study, ".RData"),
         data = map2(file, type, ~loadRData(.x, .y, "es", "studyEffects"))) %>%
  select(-file) %>%
  ## unnest effect sizes
  unnest(data)
nested_ipd3_meta

## group and nest
nested_ipd3_meta <- nested_ipd3_meta %>%
  group_by(type, Trait, Outcome, Moderator, Covariate) %>%
  nest() %>%
  ungroup()


# done <- tibble(file = list.files(sprintf("%s/results/3_ipd_meta/Bayesian/metaModels", wd))) %>%
#   separate(file, c("Outcome", "Trait", "Moderator", "Covariate"), sep = "_") %>%
#   mutate(Covariate = str_remove_all(Covariate, ".RData"),
#          done = "done")
## add in meta-moderators, which requires taking original models and 
## modifying the Moderator column
nested_ipd3_meta <- nested_ipd3_meta %>%
  filter(Moderator == "none") %>%
  select(-Moderator) %>%
  full_join(crossing(
    Trait = traits$short_name
    , Moderator = stdyModers$short_name)) %>%
  full_join(nested_ipd3_meta) %>%
  # full_join(done) %>% filter(is.na(done)) %>%
  mutate(metamod = pmap(list(data, type, Trait, Outcome, Moderator, Covariate)
                        , possibly(ipd3_meta_fun, NA_real_)))
nested_ipd3_meta
```

### Compile Results  
```{r 2 stage ipd meta run}
loadRData <- function(fileName, type, obj, folder){
#loads an RData file, and returns it
    path <- sprintf("%s/results/3_ipd_meta/%s/%s/%s", wd, type, folder, fileName)
    load(path)
    get(ls()[grepl(obj, ls())])
}

## load in effect size data 
## first get file names
nested_ipd3_meta <- tibble(type = c("Frequentist", "Bayesian")) %>%
  mutate(file = map(type, ~list.files(sprintf("%s/results/3_ipd_meta/%s/studyEffects", wd, .)))) %>%
  unnest(file) %>%
  separate(file, c("Outcome", "Trait", "Moderator", "Covariate", "study"), sep = "_", remove = F) %>% 
  filter(!is.na(study)) %>%
  ## read in the files
  mutate(study = str_remove(study, ".RData"),
         studyEff = map2(file, type, ~loadRData(.x, .y, "fx", "studySummary"))) %>%
  select(-file) %>%
  unnest(studyEff) %>%
  group_by(type, Trait, Outcome, Moderator, Covariate) %>%
  nest(studyEff = study:conf.high) %>%
  ungroup()

## now we add in the study-level moderators (i.e. meta-regression)
  
nested_ipd3_meta <- nested_ipd3_meta %>%
  filter(Moderator == "none") %>%
  select(-Moderator) %>%
  full_join(crossing(
    Trait = traits$short_name
    , Moderator = stdyModers$short_name)) %>%
  full_join(nested_ipd3_meta) %>%
  mutate(file = sprintf("%s_%s_%s_%s.RData", Outcome, Trait, Moderator, Covariate),
         metaEff = map2(file, type, ~loadRData(.x, .y, "fx", "metaSummary")),
         metaHet = map2(file, type, ~loadRData(.x, .y, "het", "metaHetero"))) %>%
  select(-file)
```

This results in a nested data frame, with columns:  

* `studyEff` = standardized study-specific effects from stage 1 regressions  
* `metaEff` = standardized meta-analytic effect from stage 2 meta-analysis  
* `metaHet` = Measures of cross-study heterogeneity  

```{r}
nested_ipd3_meta
```


#### Tables  
First, we'll combine study and meta-analytic results.  
```{r 2 stage ipd meta tables}
ipd3_meta_res <- nested_ipd3_meta %>%
  mutate(comEff = map2(studyEff, metaEff, ~(.y) %>% full_join(.x))) %>%
  select(type, Outcome, Trait, Moderator, Covariate, comEff) %>%
  unnest(comEff) %>%
  mutate(term = ifelse(term == "mods", paste0("p_value:", Moderator), term)) %>%
  filter((Moderator == "none" & term == "p_value") | 
         (Moderator != "none" & (grepl("p_value:", term)) | grepl("metamod", term))) %>%
  select(-SE, -term)
ipd3_meta_res
```

##### Study-Specific  
Next, we'll make a table of the results, separately for each moderator. To do this efficiently, we'll make a function that creates those tables across all combinations. Before calling that function, we'll do some reformatting and reshaping to get the data ready.  

```{r}
ipd3_res_tab <- ipd3_meta_res %>%
  mutate(sig = ifelse(conf.low == conf.high, "sig", "ns")) %>% # significance marker
  mutate_at(vars(estimate:conf.high), 
            ~ifelse(. < .01, sprintf("%.3f", .), sprintf("%.2f",.))) %>%
  mutate(est = sprintf("%s<br>[%s, %s]", estimate, conf.low, conf.high),
         est = ifelse(sig == "sig", sprintf("<strong>%s</strong>", est), est),
         study = factor(study, c(studies_long, "Meta-Analytic")),
         Outcome = factor(Outcome, outcomes$short_name, outcomes$long_name)) %>%
  select(type:Covariate, study, est) %>%
  pivot_wider(names_from = "Trait", values_from = "est") %>%
  select(type:study, E, A, C, N, O) %>%
  arrange(type, Outcome, Moderator, Covariate, study)
ipd3_res_tab
```

```{r}
ipd3_meta_table_fun <- function(d, type, moder, cov){
  cv <- mapvalues(cov, covars$short_name, covars$long_name, warn_missing = F)
  if(!grepl("djust", cv)) cv <- paste(cv, "Adjusted")
  md <- mapvalues(moder, c(moders$short_name, stdyModers$short_name),
                  c(moders$long_name, stdyModers$long_name), warn_missing = F)
  rs <- d %>% group_by(Outcome) %>% tally() %>% 
    mutate(end = cumsum(n), start = lag(end) + 1, start = ifelse(is.na(start), 1, start))
  cs <- rep(1,6); names(cs) <- c(" ", traits$short_name)
  cap <- if(moder == "none") {
      sprintf("<strong>Table X.</strong><br><em>Study and Meta-Analytic Estimates of %s Personality-Cognitive Domain Relationships</em>", cv) 
    } else {
      sprintf("<strong>Table X.</strong><br><em>Study and Meta-Analytic %s Moderation of %s Personality-Cognitive Domain Relationships</em>", md, cv)
    }
  tab <- d %>%
    select(-Outcome) %>%
    kable(., "html"
          , escape = F
          , booktabs = T
          , col.names = c("Study", rep("$\\beta$ [CI]", 5))
          , align = c("r", rep("c", 5))
          , caption = cap) %>%
    kable_styling(full_width = F) %>%
    add_header_above(cs) 
  for (i in 1:nrow(rs)){
    tab <- tab %>% 
      kableExtra::group_rows(rs$Outcome[i], rs$start[i], rs$end[i])
  }
  save_kable(tab, file = sprintf("%s/results/3_ipd_meta/%s/studyTables/%s_%s.RData",
                                 wd, type, moder, cov))
  return(tab)
}

ipd3_std_tab <- ipd3_res_tab %>%
  filter(!Moderator %in% stdyModers$short_name) %>%
  group_by(type, Moderator, Covariate) %>%
  nest() %>%
  ungroup() %>%
  mutate(tab = pmap(list(data, type, Moderator, Covariate), ipd3_meta_table_fun))
```

##### Meta-Analytic  

```{r}
ipd3_res_tab %>%
  filter(study == "Meta-Analytic") %>%
  group_by(type, Covariate) %>%
  nest() %>%
  ungroup()
```


## Step 4: Meta-Regressions  

For the purposes of ease, we will run all meta-regressions. However, best practice is to examine all measures of heterogeneity before making such a choice, as some metrics are overly determined by the number of studies, sample sizes in those studies, etc.  

### Table Meta-Analytic Heterogeneity  
Relative to previous tables, this is slightly complicated because Frequentist and Bayesian meta-analysis don't use the same methods for estimating heterogeneity. 
```{r}
ipd3_het_tab <- nested_ipd3_meta %>% 
  select(-studyEff, -metaEff) %>%
  mutate(Trait = factor(Trait, traits$short_name, traits$long_name),
         Outcome = factor(Outcome, outcomes$short_name, outcomes$long_name)) %>%
  arrange(type, Outcome, Trait, Moderator) %>%
  group_by(type, Moderator) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% unnest(metaHet)))
ipd3_het_tab

## frequentist
ipd3_het_tab$data[[nrow(ipd3_het_tab)]]
## bayesian
ipd3_het_tab$data[[1]]
```

```{r}
ipd3_het_tab_fun <- function(d, type, moder){
  rs <- d %>% group_by(Outcome) %>% tally() %>% 
    mutate(end = cumsum(n), start = lag(end) + 1, start = ifelse(is.na(start), 1, start))
  if(type == "Frequentist"){
    d %>%
      mutate_at(vars(tau2, QEp), ~ifelse(. < .001, "< 0.001", sprintf("%.3f", .))) %>%
      mutate_at(vars(I2:QE), ~sprintf("%.2f", .)) %>%
      select(Trait, tau2, I2, H2, QE, QEp) %>%
      kable(., "html"
            , escape = F
            , digits = 2
            , col.names = c("Trait", "$\\tau^2$", "$I^2$", "$H^2$", "<em>Q</em>", "<em>p</em>")
            , align = c("r", rep("c",5))
            , caption = sprintf("Table X. Heterogeneity estimates for %s Models with %s Moderator", type, moder)) %>%
      kable_styling(full_width = F) 
  } else{
    d %>%
      mutate_at(vars(tau2, BF), ~ifelse(. < .001, "< 0.001", sprintf("%.3f", .))) %>%
      mutate_at(vars(I2, H2), ~sprintf("%.2f", .)) %>%
      select(Trait, tau2, I2, H2, BF) %>%
      kable(., "html"
            , escape = F
            , digits = 2
            , col.names = c("Trait", "$\\tau^2$", "$I^2$", "$H^2$", "BF")
            , align = c("r", rep("c",4))
            , caption = sprintf("Table X. Heterogeneity estimates for %s Models with %s Moderator", type, moder)) %>%
      kable_styling(full_width = F) 
  }
}
```

### Functions  
#### Meta-Regression Models  

```{r 2 stage ipd meta function}
ipd3_meta_fun <- function(es, type, trait, outcome, mod, metamod){
  slmod <- if(mod %in% c("scale", "agegr")) mod else NULL
  if(type == "Bayesian") load(sprintf("%s/results/3_ipd_meta/bayes_sample_meta.RData", wd))
  # run the meta-analytic model
  mt <- if(type == "Frequentist"){
    rma(yi = Estimate
        , sei = SEI
        , ni = ni
        , mod = metamod
        , data = es)
  } else {
    update(mt
        , newdata = es
        # , save_pars = "all"
        , sample_prior = T
        , prior = prior(cauchy(0,1), class = sd)
        , iter = 4000)
  }
  save(mt, file = sprintf("%s/results/3_ipd_meta/%s/metaModels/%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod))
  
  # pull out and format the fixed effects (i.e. overall effects)
  fx <- ipd3_meta_fx_fun(mt, type)
  save(fx, file = sprintf("%s/results/3_ipd_meta/%s/metaSummary/%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod))
  
  # pull out and format the cross-study heterogeneity estimates
  het <- ipd3_meta_rx_fun(mt, type)
  save(het, file = sprintf("%s/results/3_ipd_meta/%s/metaHetero/%s_%s_%s.RData"
                          , wd, type, outcome, trait, mod))
  rm(list = c("mt", "es", "type", "trait", "outcome", "mod", "fx", "rx"))
  return(NULL)
}
```

<!--chapter:end:04-coord_meta.Rmd-->


# Method 3: One-Stage Individual Participant Analyses Reported Together  

Placeholder


## Step 1: Combine Data  
### Harmonize Data  
### Save Data Files  
## Step 2: Run Models for Each Study  
### Model Function  
### Study-Specific Simple Effects Function  
### Run Models  

<!--chapter:end:05-coord_sep.Rmd-->


# Method 3: One-Stage Individual Participant Analyses Reported Together  

Placeholder


## Comparisons Across the Taxonomy  
### Tables  
#### Fixed Effects 
#### Study-Specific  
### Figures  
#### Fixed Effects  
#### Study-Specific Effects  
## Comparisons Across Methods: Bayesian versus Frequentist  
### Tables  
#### Fixed Effects  
#### Study-Specific  
### Figures  
#### Fixed Effects  
#### Study-Specific Effects  

<!--chapter:end:06-compile-results.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:07-references.Rmd-->

